An IFS study of Low-powered Radio Galaxies

### 2018-11-07 paper.tex
correct spelling mistake

	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}. However, such galaxies are by construction extremely rare and are not representative of the general radio galaxy population. Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained. One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event. 
	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g. \citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.). If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.

@@

		We used the pre-reduced (Phase 3) datacubes from ESO. These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted. To remove this over-subtraction, we developed our own pseudo-sky subtraction routine. A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube. After checking that no stellar continuum could be fit to the medium sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.

>>>>

	There is a strong consensus within the scientific literature that the most powerful radio galaxies are the result of gas-rich, major mergers causing large amounts of material to fall on to the black hole at the centre of the resulting galaxy, thus producing an immensely powerful AGN which includes a powerful radio jet \citep[e.g.][]{Malin1983, Quillen1992, Lim2000}. However, such galaxies are extremely rare and are not representative of the general radio galaxy population. Most radio galaxies are low-powered, and their basic properties and origins are poorly constrained. One of the most popular suggestions is that they are bona-fide detections of jet-mode AGN.%, a class of AGN thought to maintain the dearth of star formation in early-type galaxies (ETGs), after most of the fuel for star formation has been removed by an earlier event. 
	These radio galaxies are known to be dusty with dust lanes having a tendency to be perpendicular to the jets \citep[e.g.][]{DeRuiter2002, VerdoesKleijn2005}. They have little ionized gas in the ISM \citep[e.g.][]{Sarzi2005}, but often have significant quantities of hot X-ray gas (e.g. \citealt{Canizares1987}; the cold phase of the ISM of radio galaxies will be examined in Ruffa et.al.\ in prep.). If the low star-formation rates typically seen in massive ETGs are preserved by jet-mode AGN, then all such ETGs must regularly go through similar active phases, and therefore low-powered radio galaxies should be much the same as their radio-quiet (quiescent phase) ETG counterparts.

@@

		We used the pre-reduced (Phase 3) datacubes from ESO. These were generally of sufficient quality for our purpose, except in both IC 1459 and IC 4296 the sky appears to have been over-subtracted. To remove this over-subtraction, we developed our own pseudo-sky subtraction routine. A median spectrum was taken from four $20 \times 20$\,spaxel regions, one in each spatial corner of the ESO reduced cube. After checking that no stellar continuum could be fit to the median sky spectrum (i.e.\ that very little light from the galaxy is contaminating the pseudo-sky regions), this median sky spectrum was subtracted from each spaxel in the cube.
